---
title: "Computed Figures from R Chunks"
subtitle: "ggplot2 in columns and full-width spans"
author:
  - name: Christopher Chizinski
    affiliations:
      - name: School of Natural Resources, University of Nebraska–Lincoln
format:
  sciposter-typst:
    poster:
      size: "42x30"
      columns: 3
      theme: unl
      # Colorblind-safe (Okabe-Ito), led by a hue that matches the theme.
      # Declaring it here is what makes it a single source: the poster chrome
      # and the R chunks below both read these values.
      palette:
        - "#D55E00"
        - "#0072B2"
        - "#009E73"
        - "#CC79A7"
        - "#E69F00"
        - "#56B4E9"
      footer:
        left: "Rendered with Quarto + Typst"
        right: "github.com/chrischizinski"
---

```{r}
#| include: false
# Read the palette declared in this document's YAML so figures and poster
# chrome can never drift apart. Falls back to Okabe-Ito if poster.palette is
# absent — R cannot see the Typst theme's built-in palette, so declaring
# poster.palette explicitly is what keeps the two in sync.
sciposter_palette <- function(n = NULL) {
  p <- rmarkdown::metadata$format$`sciposter-typst`$poster$palette
  if (is.null(p)) {
    p <- c("#0072B2", "#D55E00", "#009E73", "#CC79A7", "#E69F00", "#56B4E9")
  }
  p <- unlist(p, use.names = FALSE)
  if (is.null(n)) p else rep_len(p, n)
}
```

# In-column figure

Unsized figures fill their column width, capped at `poster.fig-max-height`
(default 45% of the column) so they cannot starve the layout.

```{r}
#| echo: false
#| message: false
#| fig-cap: "Column-width ggplot"
library(ggplot2)
# base_size 18 is a floor, not a default: axis text must stay legible at the
# 1.5m scan tier once the figure is scaled into a column.
ggplot(mtcars, aes(wt, mpg, color = factor(cyl))) +
  geom_point(size = 4) +
  scale_color_manual(values = sciposter_palette(3)) +
  labs(color = "Cylinders") +
  theme_minimal(base_size = 18)
```

# Sizing control

Set an explicit width to override the fill behavior, exactly as in any
Quarto document (`fig-width`, or a `width=` attribute on markdown images).

# Full-width span

::: {.full-width}
```{r}
#| echo: false
#| fig-cap: "Full-width histogram across all three columns"
#| fig-width: 16
#| fig-height: 4
hist(rnorm(2000), breaks = 60, col = sciposter_palette(1), border = "white", main = "")
```
:::

# Notes

Full-width blocks float to the top or bottom edge of the body — a Typst
constraint on parent-scoped floats inside columns.
