---
title: "Computed Figures from R Chunks"
subtitle: "ggplot2 in columns and full-width spans"
author:
  - name: Christopher Chizinski
    affiliations:
      - name: School of Natural Resources, University of Nebraska–Lincoln
format:
  sciposter-typst:
    poster:
      size: "42x30"
      columns: 3
      theme: unl
      footer:
        left: "Rendered with Quarto + Typst"
        right: "github.com/chrischizinski"
---

# In-column figure

Unsized figures fill their column width, capped at `poster.fig-max-height`
(default 45% of the column) so they cannot starve the layout.

```{r}
#| echo: false
#| message: false
#| fig-cap: "Column-width ggplot"
library(ggplot2)
ggplot(mtcars, aes(wt, mpg, color = factor(cyl))) +
  geom_point(size = 4) +
  scale_color_manual(values = c("#D00000", "#1f4e79", "#2e7d32")) +
  labs(color = "Cylinders") +
  theme_minimal(base_size = 18)
```

# Sizing control

Set an explicit width to override the fill behavior, exactly as in any
Quarto document (`fig-width`, or a `width=` attribute on markdown images).

# Full-width span

::: {.full-width}
```{r}
#| echo: false
#| fig-cap: "Full-width histogram across all three columns"
#| fig-width: 16
#| fig-height: 4
hist(rnorm(2000), breaks = 60, col = "#D00000", border = "white", main = "")
```
:::

# Notes

Full-width blocks float to the top or bottom edge of the body — a Typst
constraint on parent-scoped floats inside columns.
